---
title: "Lab2 Collaboration"
author: "Yealim Sung, Elcy Timothy"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question set (team)

Discuss how to approach the following questions with your teammate. When finished, both teammate should collaborate on a single `team.Rmd` file which include the answers to the following questions. 

### Tips on coordinating as a team: 
- You can start from Invididual 1 adding, committing, and pushing `team.Rmd`, and then Individual 2 can `git pull`
- Before you make changes to existing files or `git push`, remember to `git pull` first
- Coorindate with your teammate to avoid merge conflict!
- Make sure both teammates have modified `team.Rmd` file! Users who have modified this file can be viewed by issuing `git log team.Rmd` in the Terminal.


1 \. Run the following code line by line to figure out what it's doing. Then next to each line of code, write a comment explaining its purpose and function, including the use of any specific arguments. Comments in R are proceeded by a `#`, so that R knows not to run anything after the hashtag. 

For example: 
```{r,eval=FALSE}
plot(choco$Rating,choco$Cocoa.Pct, xlab = "Ratings", ylab = "Cocoa Percentage", pch = 2, cex=2) # creates a plot with Ratings on x-axis and Cocoa Percentage of y-axis. The symbol of points is set to be a triangle (pch=2) and the size of the points is adjusted to be larger (cex=2). 
```

If you are stuck, you can always go to R's help documentation. 


```{r, eval=FALSE}
recent_rating = choco[choco$Review.Date>2011,] #creates a dataframe that has choco data with Review.Date being after 2011

unique(recent_rating$Company.Location) #gives us the possible values of a factor in choco Company.Location data. The level shows the possible values of a categorical variable.

recent_rating$Company.Location = droplevels(recent_rating$Company.Location) #droplevels drops an object from which to drop unused factor levels. This line is updating the recent_rating so that it won't have any unused Company.Location levels.

head(recent_rating) #it shows us the first part of the recent_rating vector

cross_table = table(recent_rating$Review.Date,recent_rating$Company.Location) #it shows the Review.Date, Company.Location data from recent_rating vector as a table and saves that into cross_table variable.
cross_table #displays the cross_table

which(cross_table[1,]!=0 & cross_table[2,]!=0 & cross_table[3,]!=0 & cross_table[4,]!=0 & cross_table[5,]!=0) #only shows the column that does not have 0s. For example, cross_table[1,]!=0 means the first cross table that is not 0.

france_recent = subset(recent_rating,Company.Location =='France')
uk_recent = subset(recent_rating,Company.Location =='U.K.')
germany_recent = subset(recent_rating,Company.Location=='Germany') #this stores all the subsets of vectors which Company.Location is France, U.K, Germany in according variables.

par(mfrow=c(2,2)) #sets the parameter with a variable mfrow which stores column 2 and row 2
color1 = ifelse(france_recent$Rating >median(france_recent$Rating), 'blue', 'green') #sets the color blue if the Rating of france_recent dataframe is larger than the median of all the Rating of france_recent and sets the color green otherwise.
plot(france_recent$Cocoa.Pct ~ france_recent$Review.Date,ylim=c(50,90),col=color1,pch=18,cex=1.5,xlab="Review Date", ylab= "Cocoa Percentage", main= "France") #plots a dot plot with y axis limit of 50 to 90(ylim), color as the green and blue color we setted from above(col), sets the point shape as diamond which is number 18(pch), sets the scaled relative to the 1.5 which is 50% larger(cex), labels x-axis as "Review Date"(xlab), labels y-axis as "Cocoa Percentage"(ylab), and looks the data from "France" dataframe(main).
legend('bottomright',legend=c('High Rating', 'Low Rating'),col=c('blue','green'),pch=18) #sets the legend to be positioned on bottom right, shows High Rating and Low Rating, sets the column color blue and green, and sets the point shape as diamond like above.

color2 = ifelse(uk_recent$Rating >median(uk_recent$Rating), 'purple', 'red') #sets another color set where it is purple when uk_recent Rating is larger than the median of the whole uk_recent Rating and red otherwise.
plot(uk_recent$Cocoa.Pct ~ uk_recent$Review.Date,ylim=c(50,90),col=color2,pch=18,cex=1.5, xlab="Review Date", ylab= "Cocoa Percentage", main= "UK") #plots a dot plot with y axis limit of 50 to 90(ylim), color as the purle and red color we setted from above(col), sets the point shape as diamond which is number 18(pch), sets the scaled relative to the 1.5 which is 50% larger(cex), labels x-axis as "Review Date"(xlab), labels y-axis as "Cocoa Percentage"(ylab), and looks the data from "UK" dataframe(main).
legend('bottomright',legend=c('High Rating', 'Low Rating'),col=c('purple','red'),pch=18) #sets the legend to be positioned on bottom right, shows High Rating and Low Rating, sets the column color purple and red, and sets the point shape as diamond like above.

color3 = ifelse(germany_recent$Rating > median(germany_recent$Rating), 'orange', 'yellow') #sets another color set where it is orange when uk_recent Rating is larger than the median of the whole uk_recent Rating and yellow otherwise.
plot(germany_recent$Cocoa.Pct ~ germany_recent$Review.Date,ylim=c(50,90),col=color3,pch=18,cex=1.5,xlab="Review Date", ylab= "Cocoa Percentage", main= "Germany") #plots a dot plot with y axis limit of 50 to 90(ylim), color as the orange and yellow color we setted from above(col), sets the point shape as diamond which is number 18(pch), sets the scaled relative to the 1.5 which is 50% larger(cex), labels x-axis as "Review Date"(xlab), labels y-axis as "Cocoa Percentage"(ylab), and looks the data from "Germany" dataframe(main).
legend('bottomright',legend=c('High Rating', 'Low Rating'),col=c('orange','yellow'),pch=18) #sets the legend to be positioned on bottom right, shows High Rating and Low Rating, sets the column color orange and yellow, and sets the point shape as diamond like above.
```

2 \. Click Zoom on the Rstudio window (under Plots) to see the plot more clearly. How do you think the plot produced from the code above can be improved? Recommend at least one possible improvement. 

- Germany's Figure margins are too large. Also suggest to set the y limit as 60 up to 90 to remove the white space at the bottom of the chart. 

3 \. How does the **number** of ratings (not the actual value of the rating) depend on the year? Use graphics to answer this question.
```{r}
choco <- read.csv("https://raw.githubusercontent.com/lbchu/ds202_labs/master/choco.csv")
plot(choco$Review.Date, choco$Rating)
```

- As you can see from above, it seems like 2006 and 2008 had more number of ratings compared to later years. The number of ratings are decreasing year by year.

4 \. How do ratings compare across different company locations? Focus on the three locations with the most ratings. Hint: the function `sort()` might come in handy here.
```{r}
##order(choco$Company.Location)
temp = choco[order(choco$Rating),]
head(temp)
Loc1 = choco[choco$Company.Location == "Canada",]
Loc2 = choco[choco$Company.Location == "U.S.A.",]
Loc3 = choco[choco$Company.Location == "France",]
z <- c("Canada","U.S.A.","France")
boxplot(Loc1$Rating, Loc2$Rating,Loc3$Rating, xlab="Country", ylab = 'Rating', main = "Rating Distribution of top 3 countries", names = z)
```


5 \. Brainstorm and write down an interesting question that can be answer from the dataset. The question should not duplicate the questions above.

- Does the specific bean origin affect the ratings? If it does, which origin has the highest average rating?

6 \. Bonus points (optional): Answer the question from the dataset.